Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-14 paper/structureScene.tex
write more of my biography + punctuation in gl's biography

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie and the Ircam in Paris, France, in 2013. Since 2013, he is a PhD student at ENS in Paris.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lafay}}]{Gr\'egoire Lafay} was born in Paris, France, in 1990. He received in 2011 the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre and Marie Curie and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D student at IRCCyN, a French laboratory dedicated to cybernetics. His current research interests include acoustic scene similarity and classification, as well as acoustic scene perception. 
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received an engineering degree from TELECOM ParisTech in 2013 and M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie and the Ircam (UPMC) in Paris, France, in 2013. Since 2013, he is a Ph.D. student at \'{E}cole normale sup\'{e}rieure in Paris, working under the supervision of St\'{e}phane Mallat.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lafay}}]{Gr\'egoire Lafay} was born in Paris, France, in 1990. He received in 2011 the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre and Marie Curie and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D. student at IRCCyN, a French laboratory dedicated to cybernetics. His research interests include acoustic scene similarity and classification as well as acoustic scene perception. 
\end{IEEEbiography}
